---
title: "Tutorial 12"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(readxl)
HW_7_part_5_number_4 <-read_excel("~/Documents/MTH_142/Tutorials/12th_Rtutorial_ANOVA/HW_7_part_5_number_4.xlsx")
library(tidyverse)
library(mosaic)
```

## Introduction

In this tutorial, We'll format homework problems so that they can be put into R to complete an ANOVA test. We'll, of course, also do this with a data set. Your assignment is on the last page.

## ANOVA from a HW problem

Here's the text from the HW problem:

*Is a statistics class' delivery type a factor in how well students do on the final exam? The table below shows the average percent on final exams from several randomly selected classes that used the different delivery types.*

1.  The `mosaic` and `openintro` libraries have been preloaded.

2.  Go to HW 7 part 5 Number 4. My version of the data has been preloaded as HW_7\_part_5\_number_4.Run the chunk below to see it.

```{r HW-ANOVA, exercise=TRUE}
HW_7_part_5_number_4
```

## Pivot the table in R

We need to reorganize the table so there are two columns. I'll do this first in R with some code then redo it in excel by copy and pasting. The first column I'll call `meeting_type` and will have the levels: `Face-to-Face`,`Hybrid`,`Online`. The second I'll call `final_grades` which will have all the values in it.

We need a function from a new `library(tidyverse)`. It is called `pivot_longer()` and takes `data`, `cols` or column names, the name of the new leveled column with `names_to` and the name of the new column with values in it called `values_to`. finally we have to save the new table with the `<-` operator.

```{r pivoted-table, exercise=TRUE}
#This will make the two columns of the new "pivoted table" and save it as problem_4_pivoted

problem_4_pivoted<- 
  pivot_longer(
  data = HW_7_part_5_number_4,
  cols = c("Face-to-Face","Hybrid","Online"), 
  names_to = "meeting_type",
  values_to = "final_grades"
  )

#This displayed the table so we can see it. 
problem_4_pivoted
```

## Or pivot the table as a spreadsheet

We need to reorganize the table so there are two columns. I'll do this first in R with some code then redo it in excel by copy and pasting. The first column I'll call `meeting_type` and will have the levels: `Face-to-Face`,`Hybrid`,`Online`. The second I'll call `final_grades` which will have all the values in it.

1.  Open a spread sheet application and paste the data in.
2.  We will have to format the data so one column is the levels and one is the values. (see video)
3.  Save the spreadsheet and upload the sheet to R.
4.  Import the data by double clicking the spreadsheet and choosing import.

## Run the test in R

We have to check three things before we can run ANOVA

1.  The observations are independent within and across groups.
2.  The data within each group are nearly normal.
3.  The variability across the groups is about equal.

Luckily the problem tells us to assume these work out.

1.  Now we must run the analysis. To execute and save the results type: `result_problem_4 <- aov(final_grades~meeting_type,data=problem_4_pivoted)`

```{r ANOVA-setup}


problem_4_pivoted<- 
  pivot_longer(
  data = HW_7_part_5_number_4,
  cols = c("Face-to-Face","Hybrid","Online"), 
  names_to = "meeting_type",
  values_to = "final_grades"
  )
```

```{r ANOVA, exercise=TRUE}

```

2.  You can look at the results by adding `result_problem_4` but it doesn't tell you much. To see the actual results type:

    `anova(result_problem_4)`

    in the chunk above.

## ANOVA from a dataset

1\. Check out the `HELPrct` dataset. Read about it with`?HELPrct`

```{r help-look, exercise=TRUE}
HELPrct
```

We'll examine the `cesd` and `substance` variables. Specifically we I'd like to know if there is any difference in the average baseline depression measure based on current substance use.

Let's verify:

1.  The observations are independent within and across groups.
2.  The data within each group are nearly normal.
3.  The variability across the groups is about equal.

To check if the data is roughly normal let us check out the box plots with gf_boxplot() and some statistics with favstats(). Input the code in the chunk below.

```{r help-stats,exercise = TRUE}


```

```{r help-stats-hint}
gf_boxplot(cesd~substance,data=HELPrct)
favstats(cesd~substance,data=HELPrct)
```

There is just one outlier in the Heroin and its not particularly extreme so let's proceed.

4.  There are three groups, and we are testing three means of each group the hypothesis notation looks like:

$H_0: \mu_a = \mu_c =\mu_h$

$H_1: \mu_a \ne \mu_c \ne \mu_h$

$\alpha =0.05$

5.  In the chunk below have R do the computation for the test with `aov()` and save the results, then show the output with `anova()`

```{r anova-helprct, exercise=TRUE}

results_substance <- aov(  ,data=)


anova()
```

```{r anova-helprct-hint}
results_substance <- aov(cesd~substance,data=HELPrct)


anova(results_substance)
```

## Assignment

5 points

-   Use the `yrbss` data set.

-   You are to perform an ANOVA test to test if the average number of days the children are active varies by race.

-   Before your test you should verify that the standard deviations are about the same using favstats(), discuss independence, and look at a boxplot for normality and outliers

-   Write up the conclusion of your test.
