---
title: "Tutorial 6"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(mosaic)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

We want to be able to calculate how likely an event is from a given distribution. In this tutorial we'll focus on how to calculate probabilities from the binomial, and normal distributions. This tutorial is split into two parts: Part 1 is the Normal distribution and Part 2 is the Binomial Distribution. There is no assignment associated with this tutorial.

## Part 1: Normal Distribution

1.  Open Rstudio and load the mosaic package. Open the MTH 142 cheat sheet.

2.  Let's look at Homework 4 part 1 number 1. I'll type:

`xpnorm(-1.35,mean=0,sd=1)`

3.  To do number 1 part c. We have to do abit more work:

-   We have to calculate the area lower than the z-score -0.4 with `xpnorm(-0.4,mean=0,sd=1)`
-   We also have to calculate the area lower than 1.5. `xpnorm(1.5,mean=0,sd=1)`
-   Then we have to subtract those two numbers to find the area in the middle.

Type one line of code that will combine all three bullets above.

```{r norm-prob, exercise=TRUE, exercise.eval=TRUE}

```

```{r norm-prob-hint}
xpnorm(1.5,mean=0,sd=1) - xpnorm(-0.4,mean=0,sd=1) 
```

Note: In the video I also go into number 1 part d.

4.  Question 3 part a in the same assignment is asking about quantile (aka a percentile). We have to use `xqnorm(0.80,mean=153,sd=7.67)`

## Part 2: Binomial Distribution

1.  Open Rstudio and load the mosaic package. Open the MTH 142 cheat sheet.

2.  Let's look at Homework 4 part 2 number 1. Here is the text from the problem:

### Data collected by the Substance Abuse and Mental Health Services Administration (SAMSHA) suggests that 69.7% of 18-20 year olds consumed alcoholic beverages in 2008.

To view the graph of the binomial distribution run the chunk below.

```{r binom-dist-plot, exercise= TRUE}
plotDist("binom", size = 10, prob= 0.697)

```

3.  In part b we are asked to calculate the probability that exactly 6 18-20 year olds drink Alcohol we can do this with the density binomial function `dbinom(6, size =10, prob=0.697)`.

```{r binom-dist-exact-6, exercise=TRUE}
dbinom(6, size =10, prob=0.697)

```

4.  To calculate the probability that up to 6 18-20 year olds drink we would do `pbinom(6,size=10,prob=0.697)` . This is the same as calculating the probability that 0,1,2,3,4,5 or 6 drink with dbinom().

```{r binom-dist-up-to-6, exercise = TRUE}
# To get the probability of up to 6 people drink use either code below. 

pbinom(6, size =10, prob=0.697)


dbinom(0, size =10, prob=0.697) + 
  dbinom(1, size =10, prob=0.697)+ 
  dbinom(2, size =10, prob=0.697)+ 
  dbinom(3, size =10, prob=0.697) + 
  dbinom(4, size =10, prob=0.697) +
  dbinom(5, size =10, prob=0.697) + 
  dbinom(6, size =10, prob=0.697)
```

You will have to get creative in answering other questions, if you need help post in the forums.

## No Assignment
