---
title: "Tutorial 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(mosaic)
library(openintro)
library(shiny)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This tutorial should be completed after the chapter 1 reading.
Specifically you should have read about the different types of
variables.

We are going to consider the `loan50` data frame from chapter 1 in the
text. More detail is given in the video called "First R tutorial." Your
assignment is on the last page.

## Exploring the Data

1.  Read about the data. (Summary on page 12 in the text. [More info on
    openintro.org](https://www.openintro.org/data/index.php?data=loan50)
    ).

2.  Load the following libraries and prevent scientific notation by
    copying and pasting the following into the chunk below: 
    -   library(openintro) 
    -   library(mosaic)
    -   library(tidyverse) 
    -   options(scipen=10)

```{r load-libraries, exercise= TRUE}

```

4.  We want to look at the loan50 data. Below are three ways of doing
    this. Type and run each:
    -   loan50

    -   glimpse(loan50)

    -   head(loan50)

```{r look-loan50, exercise= TRUE, exercise.lines = 3}

```

5.  Questions:

```{r quiz}
quiz(
  question("How many observations are in the data set?",
    answer("50", correct = TRUE),
    answer("18"),
    answer("6"),
    answer("0")
  ),
  question("How many variables are in the dataset",
    answer("50"),
    answer("18", correct = TRUE),
    answer("6"),
    answer("0")
  ),
  question("Which expressions show the variable is numeric?",
    answer("fct"),
    answer("dbl", correct = TRUE),
    answer("int", correct = TRUE),
    answer("chr")
  )
)
```

6.  What do we want to learn about lending club borrowers from the tables of data?

## Graphing

### Categorical

To start we'll use `gf_bar()` to graph the categorical variable `state`.
Fill in the add the variable and dataframe names then run the
chunk below.

```{r gf-bar, exercise = TRUE}
gf_bar(~,data=)
```

```{r gf-bar-hint}
gf_bar(~state,data=loan50)
```

If you want to learn more about `gf_bar()` type `?gf_bar()` in the chunk
below.

```{r help-gf-bar, exercise = TRUE}

```

### Numeric

Let's use `gf_histogram()` to graph `emp_length` from the `loan50`
dataframe.

```{r gf-hist, exercise = TRUE}

```

```{r gf-hist-hint}

gf_histogram(~"variable_name",data="data frame name")

# remove the quotations and type the variable and data in their appropriate locations. 
```

### Go back to the graphs above and add an x-axis label, a title and some color.


See your assignment below 

## Assignment

### Part 1. 4 points

In a new Rmarkdown file.

-   Choose one categorical or numeric variable from loan50 and make a bar chart or histogram. You cannot use the state or emp_length variable.

-   If categorical: state whether the variable is (ordinal or nominal). If numeric: state wether it is discrete or continuous and why.3

-   Output the Rmarkdown file as html (be sure to see the 1st R tutorial for this).

-   Post these in the the second Rtutorial forum.

### Part 2. 1 point

For this part of the assignment you are to post a reply to a classmate's assignment.

Do you agree or disagree that the variable is the correct type? Why?

