---
title: "Tutorial 14"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(mosaic)
library(openintro)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

In this R Tutorial we'll walk through the process of making a linear regression model in R

## Organize Data

1.  The `mosaic` and `openintro` libraries have been preloaded.

2.  I'll be working from question 1 in homework 8 part 2. Here's the text from that assignment:

*The data below was collected from manufacturer advertisements of their vehicles horsepower and highway gas mileage (mpg.). Use this data to answer the following questions.*

The data from my version of the problem is below*, rename the vectors `x` and `y` as `horsepower` and `mpg`. 

```{r data-input,exercise=TRUE}
x <- c(158, 250, 340, 350, 390, 190, 220)
y <- c(33, 28, 15, 17, 11, 35, 42)

```

```{r data-input-hint}
hp <- c(158, 250, 340, 350, 390, 190, 220)
mpg <- c(33, 28, 15, 17, 11, 35, 42)

```

\* We could have imported the data as a table but this felt faster. See tutorial 4 for information on that. 

## Make a scatter plot and linear regression

1. In the chunk below make a scatter plot using `gf_point()` of `mpg` vs `hp`. 

```{r prepare-scatter}
hp <- c(158, 250, 340, 350, 390, 190, 220)
mpg <- c(33, 28, 15, 17, 11, 35, 42)
```

```{r scatter-plot, exercise=TRUE, exercise.setup="prepare-scatter"}
#Note you don't need a data argument because we're dealing with two vectors, not a data frame. 
gf_point(____~____)

```

```{r scatter-plot-hint}
gf_point(hp~mpg)

```

2. We can add a regression line by piping `gf_point()` to `gf_lm()` with `%>%` .



```{r line-plot, exercise=TRUE, exercise.setup="prepare-scatter"}
#Note you don't need a data argument because we're dealing with two vectors, not a data frame. 
gf_point(____~____) %>%
  gf_lm(____~____)

```

```{r line-plot-hint}
gf_point(hp~mpg) %>%
  gf_lm(hp~mpg)

```

You should add better axes labels and a good title. IN case you forget you can add this with the arguments `title= "title" `, `xlab= ""`,`ylab= ""` to the argument of `gf_point()`.

## Find the correlation coefficient and equation. 

1. We can use the `lm()` to find the linear model that fits our data.  

```{r lm, exercise=TRUE}
hp_mpg_model <- lm(hp~mpg)
hp_mpg_model
```

2. From the output of the model we can see that the equation is

$y=-6.896 x + 449.448$ 

where x is mpg and y is hp. 

3. We can also use `msummary(hp_mpg_model)` to see the p-value for a hypothesis and the $r^2$ value. To see the correlation coefficient take the square root of r^2 or use `cor()`. Also note we can see the intercept and mpg values that we used to write the linear equation. 

```{r summary-setup}
hp_mpg_model <- lm(hp~mpg)
hp_mpg_model
```

```{r summary, exercise=TRUE}
msummary()
sqrt()
cor()
```

```{r summary-hint}
msummary(hp_mpg_model)

#When taking the square root of r^2 you have to consider the sign + or - of r.  
sqrt(0.8171)

cor(hp~mpg)
```



Step 7. Notice when I knitted I needed to bring the data into R I did this by adding the following to the setup chunk.

library(readxl) Rtut_13 \<- read_excel("Rtut_13.xlsx")

## Assignment 

5 points

Make a linear regression model for `Age` vs `Price` from the `Mustangs` data frame from the `mosaic` package. 

Give the equation, correlation coefficient, a title, and good x and y axes labels. 

Knit your document as an html and post it to the forum. 
