---
title: "Tutorial 8"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(openintro)
library(mosaic)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

In this tutorial I will show you how to use the `count()` and `tally()` functions. We'll use data from [OpenIntro](https://www.openintro.org/data/) .

## tally() and count()

1.  You will need to load the `mosaic` library for the functions and `openintro` for the data.

```{r print-limit, exercise=TRUE, exercise.lines=3}
library()
library()
```

2.  The tally() function will count the number of responses for you. My variable is `coal_mining` from the `pew_energy_2018` data list \*. In the chunk below evaluate `tally()` by inputting the variable and data.

```{r tally, exercise=TRUE, exercise.eval=FALSE}
tally()
```

```{r tally-hint}
tally(~coal_mining, data=pew_energy_2018)
```

You can also use the `count()` function it does almost the same thing. Change `tally` to `count` in the chunk above.

\* For whatever reason the authors of the OpenIntro data did not make pew_energy_2018 into a dataframe, to make it one type:

`pew_energy_dataframe <- as.data.frame(pew_energy_2018)`

You'll need to do this in the setup chunk of the project.

## No Assignment

You don't have to turn in anything special for this tutorial.
