---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(readxl)
Problem_1_data <- read_excel("~/Documents/MTH_142/Tutorials/11th_Rtutorial_diff_or_means/Problem-1-data.xlsx")
library(mosaic)
library(openintro)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

In this tutorial we'll use data from a homework problem to do a difference of means t.test. We will do this two times: once from a homework problem and once from a data set. Your assignment is on the last page.

## Diff of means with two vectors containing data

1.  Import data from a homework problem. I've done this in the background for this tutorial, if you need a refresher see Rtutorial 4. I've named the Data `Problem_1_data`. Here's the text from that problem from the OpenIntro Text

### "Durable press" cotton fabrics are treated to improve their recovery from wrinkles after washing. "Wrinkle recovery angle" measures how well a fabric recovers from wrinkles. Higher is better. Here are data on the wrinkle recovery angle (in degrees) for a random sample of fabric specimens. Assume the populations are approximately normally distributed with unequal variances. A manufacturer believes that the mean wrinkle recovery angle for Hylite is better. A random sample of 25 Permafresh (group 1) and 20 Hylite (group 2) were measured. Test the claim using a 10% level of significance.

2.  For Independence we have to assume that no piece was sampled more than once. The problem states the data is normal. We can proceed.

3.  The Hypothesis notation and alpha are

$H_0: \mu_p = \mu_h$

$H_0: \mu_p < \mu_h$

$\alpha = 0.10$

2.  The data was imported into R as a list so each treatment is a vector and we can call the vector with the `$` operator. With the code below we are doing a difference of means test between Hylite and Permafresh. The null hypothesis is that the difference should be 0. Note that the alternative= "less" because the manufacture thinks that Hylite is better and I listed Hylite second in the `t.test()`.

```{r t-test,exercise=TRUE}
t.test(x=Problem_1_data$Permafresh, y=Problem_1_data$Hylite,mu=0,alternative = "less")
```

The p-value is 0.0008659 which is much less than $\alpha=0.10$ so we reject the null in favor of the alternative.

## Diff of means with tidy data frame

Let's do this process again with a dataset

1. Take a look at the nyc_marathon dataset.

```{r look, exercise= TRUE}

```

```{r look-hint, exercise= TRUE}
View(nyc_marathon)
?nyc_marathon
```

2. We might want to see if there is a difference in the two average winning times for men's and women's category at the 5% signifigance level. Our notation would look like this:

$H_0: \mu_m = \mu_h$

$H_0: \mu_p < \mu_h$

$\alpha = 0.10$

3. Take a look at the data again. Notice that `Men` and `Women` are in the same column in the variable `division`. These are called the levels of `division`. We used them in the 3rd_Rtutorial We'll use them to run our test. 

```{r nyc-t-test,exercise}
t.test(time_hrs~division,data=nyc_marathon, mu=0,alternative="two.sided")
```

There's scientific notation again, turn it off with `options(scipen=10)` or regonize that number rounds to 0. 

The p-value is much less than alpha we reject the null and state that there is a difference. 

## Outliers!

We do not yet know how to remove outliers, but the data frame from our hypothesis test had some. Run `gf_boxplot()` to see them. 

```{r outliers, exercise=TRUE}
gf_boxplot(time_hrs~division,data=nyc_marathon)
```

We should not have run this test, because our data wasn't normal. We didn't even verify independence... 

For shame, now I don't know if the results of my test mean anything.  

## Assignment

5 points

In an Rmarkdown file:

Use the `satgpa` dataset in the `openintro` package. 

Set up a hypothesis test to see if there is a difference between sexes on the numeric variable of your choosing. 

Don't forget to discuss independence and normality. If you do find outliers choose another variable. The formatting is a bit different because the `sex` variable is numeric in this data frame. Use either of the below formats to make your boxplots 

-   `gf_boxplot(~sat_v|sex,data=satgpa)`    
-   `gf_boxplot(sat_v~sex,group=~sex,data=satgpa)`

There is an outline available if you want to use it. 

