---
title: "Tutorial 5"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(openintro)
library(mosaic)
knitr::opts_chunk$set(echo = FALSE)
```


## Introduction 

In this tutorial you will make a histogram, a boxplot, and run `favstats()` broken up by variable levels. Post questions in the forums. Your assignment is on the last page. 


## Make a histogram

We make a histogram back in 2nd Rtutorial, remember to use gf_histogram() our variable must be numeric. 

1. For this document tutorial we’ll use the `run17` dataframe from `openintro`. Read about it here. Load the libraries in the chunk below.

```{r library, exercise = TRUE}

```

```{r library-hint}
library(openintro)
library(mosaic)
```

2. Let's look at `run17` with the chunk below.

```{r look, exercise = TRUE}

```

```{r look-hint}
glimpse(run17)
```

Lets make a histogram of `net_sec`

```{r net-sec-hist, exercise= TRUE}
gf_histogram(~,data=)
```

```{r net-sec-hist-hint}
gf_histogram(~net_sec,data=run17)
```

Notice the two humps in the graph. Those are for the different races. Let's facet these two races to examine them better. 

```{r net-sec-hist-facet,exercise=TRUE}
gf_histogram(~net_sec|event,data=run17)
```

We can further break this data apart by sex to see how the times were different for `F` and `M`. Let's add `fill=~sex` as an argument.  `sex` is a variable so it needs the \~ .

```{r net-sec-hist-sex,exercise=TRUE}
gf_histogram(~net_sec|event,data=run17,fill=~sex)

```

Now it looks like many more females ran the race than males. This is not necessarily true. The default position of the bins in a histogram is "stack"-ed, but we can change it to dodge for a better comparison. 

Using the chunk below type `position="dodge"` as an argument. Notice that the y-axis get much shorter. 

Now change position = "identity" and alter the transparency with `alpha=0.3` and change the outline to "black" with the color argument. Try it in the chunk below. 

```{r net-sec-hist-identity,exercise=TRUE}
gf_histogram(~net_sec|event,data=run17,fill=~sex,position="")

gf_histogram(~net_sec|event,data=run17,fill=~sex,position="",alpha=,color="")
```

```{r net-sec-hist-identity-hint}
gf_histogram(~net_sec|event,data=run17,fill=~sex,position="dodge")

gf_histogram(~net_sec|event,data=run17,fill=~sex,position="identity",alpha=0.3,color="black")
```

```{r quiz}
quiz(
  question("The peak of the male histogram is shifted slightly to the left in the 10 mile run. What does this mean?",
    answer("There were more women in the race"),
    answer("The men ran faster in the 10 mile run", correct=TRUE),
    answer("It means nothing"),
    answer("codetools")
  ),
  question("The 10 mile race is much more popular than the 5k",
    answer("True", correct = TRUE),
    answer("False"),
    answer("Impossible to tell")
  ),
   question("The skew in 5 k race...",
    answer("is toward the right tail", correct = TRUE),
    answer("means the mean is less than the median", correct= TRUE),
    answer("means there may be some slower runner which would be outliers", correct= TRUE)
  )

)
```


## Boxplot

We will quickly make a boxplot of the same data. Below is the last chunk from the previous topic. Change histogram to boxplot. Both boxplot and histograms take a single numeric variable, so we can quickly switch between the two. 

```{r net-sec-boxplot,exercise=TRUE}
gf_histogram(~net_sec|event,data=run17,fill=~sex,position="dodge")

gf_histogram(~net_sec|event,data=run17,fill=~sex,position="identity",alpha=0.3,color="black")
```

I think the position= "dodge" is more helpful here. Infact it is the default position for a boxplot so we do not need to add it at all.

## favstats()

Take the code above and change `gf_boxplot` to favstats. You'll have to delete the position and alpha and color because favstats is not a graph. Also we want to change `event` to `sex`. 

```{r net-sec-favstats,exercise=TRUE}
gf_boxplot(~net_sec|event,data=run17,fill=~sex,position="dodge")

```

```{r net-sec-favstats-hint}
favstats(~net_sec|sex,data=run17)

```

## Assignment

	Part 1. 5 points
 
You are to create a html file from an Rmarkdown file.

-   You will use the `run12` data from the openintro library. In words describe the data. (use ?run12)
-   Create a histogram with one variable of your choosing from above (note that you need a numeric variable for this).Your histogram must be broken up by the levels of `gender`. You do not need to facet this histogram. 
-   Also make a boxplot of the data broken up by `gender`. 
-   Run favstats() also split up by `gender`.
-   Do an three sentence analysis using the statistics language we’ve been learning over the last three chapters.
-   Output your Rmarkdown file as an html document and post it to the forum.