---
title: "Tutorial 7"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(mosaic)
library(openintro)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

In this tutorial I will show you how to calculate confidence intervals from a binomial distribution. We will do it twice. Once from a problem from HW 5 part 1 and again from the `exclusive_relationship` data set in the `openintro` library. We'll be using a problem from the [[OpenIntro]{.underline} Textbook](https://www.openintro.org/book/os/). Your assignment is on the last page.

## C.I. From Statistics

1.  Find HW 5 part 1 number 5. Here's the text of the problem:

*A store randomly samples 603 shoppers over the course of a year and finds that 142 of them made their visit because of a coupon they'd received in the mail. Construct a 95% confidence interval for the fraction of all shoppers during the year whose visit was because of a coupon they'd received in the mail.*

2.  Load `library(mosaic)`. Open the MTH 142 cheat sheet and find `prop.test()`. Type `?prop.test()` to see the arguemnts required.

```{r libraries, exercise=TRUE, exercise.eval=FALSE}

```

3.  To make a confidence interval type `prop.test(x=142,n=603, conf.level=0.95, correct= "FALSE")`

Try it in the chunk below.

```{r prop-test, exercise=TRUE, exercise.eval=FALSE}
prop.test()
```

Find the values that correspond to the confidence interval.

## C.I. From Data

Let's find a confidence interval from a data set.

1.  Load `library(openintro)` in the chunk below and type `?exclusive_relationship` to read about that data frame.

```{r exclusive-relationship, exercise=TRUE, exercise.eval=FALSE, exercise.lines=3}
library()
```

2.  It might make sense to take a look at the data itself, do that in the previous chunk.\*

3.  I want to know the true proportion of students who have had 1 exclusive relationship (aka the parameter). Since the binomial distribution is based on successes, we have to tell R what represents a success. The variable that has the successes is `num`. Make a 90% C.I. for the number of students that have had one exclusive relationships by typing \~num==1. Try it below.

```{r exclusive-relationship-0, exercise=TRUE, exercise.eval=FALSE, exercise.lines=3}
prop.test(~num ==______,data=_______,conf.level=, correct= "FALSE")
```

```{r exclusive-relationship-0-hint}
prop.test(~num == 1,data=exclusive_relationship,conf.level=0.90, correct= "FALSE")
```

\* If you want to use `view()` or `head()` to look at the data load the tidyverse. Otherwise just type `exclusive_relationship`

## Assignment

5 points.

In an Rmarkdown file:

-   Verify independence and the success-failure condition.

-   Use the `exclusive_relationship` data frame to make a 90% confidence interval for a different number of relationships (Not 1, I just did that. 0 is also weird, don't do that one).

-   Interpret your confidence interval in a sentence.

-   Suppose that someone told you the true proportion of students in the number of exclusive relationships that you chose is 15%. Would you agree based on your confidence interval. Why or why not?

Knit your file as a pdf and submit it to the forums.
