---
title: "Tutorial 3"
output: learnr::tutorial
runtime: shiny_prerendered
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(learnr)
library(shiny)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

We are going to consider some fastfood data set from openintro.org. I'll
show how to use the mosaic package to calculate summary statistics and
gf_boxplot to make box plots. Your assignment is on the last page.

1.  read about the data set. ([see
    openintro.org](https://www.openintro.org/data/index.php?data=fastfood))

2.  Load the openintro library for the data and the mosaic library for
    the functions by typing them into the console.

```{r libraries, exercise = TRUE }

```

```{r libraries-hint}
library(openintro)
library(mosaic)
```

## Sample Statistics

3.  We want to look at the fastfood data. We saw several ways to do this
    in the first R tutorial. Type one into the chunk below.

```{r look, exercise = TRUE }

```

```{r look-hint}
glimpse(fastfood)
```

```{r quiz-varaible}
quiz(
  question("What type of variable is calories",
    answer("dbl"),
    answer("numeric continuous"),
    answer("numeric discrete", correct = TRUE),
    answer("categorical nomial"),
    answer("categorical ordinal" )
  ),
  question("What type of variable is restaurant",
    answer("chr"),
    answer("numeric continuous"),
    answer("numeric discrete"),
    answer("categorical nomial", correct = TRUE),
    answer("categorical ordinal" )
  )
)
```

4.  Let's find some sample statistics. favstats() from the mosaic
    library will spit out the normal summary statistics. You can see the
    all the statistics you need document for more functions we can use
    here.

```{r summary-stats, exercise = TRUE}
favstats(~calories,data=fastfood)
```

5.  Notice the `calories` are all over the place from 20 to 2430, this
    is caused by the different types of foods from salads to burgers to
    fries. We should edit the formula to break the food into
    restaurants.

```{r summary-stats-rest, exercise = TRUE}
favstats(calories~restaurant,data=fastfood)
```

```{r quiz}
quiz(
  question("How many food items from McDonalds are in the data?",
    answer("140"),
    answer("540"),
    answer("57", correct = TRUE),
    answer("none of the above")
  ),
  question("On average which resturant has items with the least calories",
    answer("Chick Fil-A", correct=TRUE),
    answer("Burger King"),
    answer("McDonalds"),
    answer("Subway")
  ),
  question("Which resturant has the largest spread of calories?",
    answer("Chick Fil-A"),
    answer("Burger King"),
    answer("McDonalds", correct=TRUE),
    answer("Subway")
  )
)
```

## Boxplots

We can view these five number summaries as boxplots. Copy the chunk from
above and change favstats() to gf_boxplot().

```{r boxplot, exercise = TRUE}

```

```{r boxplot-hint}
gf_boxplot(calories~restaurant,data=fastfood)
```

Note the outliers. We will learn how to remove those much later in the
course. The coef defaults to 1.5 but we can change our coef for the
outlier whiskers by adding `coef =3` as an argument to `gf_boxplot()`.
Try it.

```{r coef, exercise=TRUE}
gf_boxplot(calories~restaurant,data=fastfood)

```

```{r coef-hint}
gf_boxplot(calories~restaurant,data=fastfood,coef = 3)

```

To see all the things to change type `?gf_boxplot()` into a chunk. Try
to give a good title, change the color, and improve the axes labels.

## Assignment

### Part 1. 5 points

Make a new .Rmd document. Then choose another numeric variable and
generate a new box and whisker plot from the `fastfood` data frame. You
cannot use `calories`. Then you will:

-   Make the box and whisker plot a pretty color

-   Add a good title

-   knit (or render) it as html

-   Upload it to the 3rd rtutorial forum.

To see which attributes you can change in `gf_boxplot()` type
`?gf_boxplot`. To see which colors you can use type `colors()` into the
console (You can see me do this in the video).
